A comparison of single-cell trajectory inference methods: towards more accurate and robust tools

### 2018-04-03 analysis/paper/paper.Rmd
update paper

## Data and code availability
The datasets used in this study are deposited in zenodo [doi.org/10.5281/zenodo.1211533](doi.org/10.5281/zenodo.1211533). Code is available as several R packages on github [https://github.com/dynverse/dynverse](https://github.com/dynverse/dynverse).

>>>>

## Data and code availability
The datasets used in this study are deposited in zenodo [doi.org/10.5281/zenodo.1211533](https://doi.org/10.5281/zenodo.1211533). Code is available as several R packages on github [github.com/dynverse/dynverse](https://github.com/dynverse/dynverse).
